MCTS Applied to Co-operative Problems

### 2015-08-06 Report/response.tex

``The \emph{Agents} are provided with a forward model, that allows simulation of potential moves up to the end of the game. The \emph{Agents} are not allowed to directly query any information about the game state other than the score at any given state (current or simulated).''
\paragraph*{\textit{If an agent reaches a goal, is it known to the other agents?}}
We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.

``All \emph{Agents} are aware of the current score achieved, and therefore can calculate if a \emph{Goal} is reached.''

\paragraph*{\textit{In what sense this domain interesting compared to other domains?}}
We feel that this problem domain is interesting due to placing each agent that is typically designed to solve problems by themselves in an environment where they must rely on another agent performing certain sequences of actions. To quote the words of Reviewer F ``\textit{This proves to be an interesting reward space to explore, given that we are dealing with circumstances where players need to take action then await the outcome courtesy of another player}''. The domain also gains an interesting aspect when we consider the ability to, in a slowed down pace, allow human players to potentially communicate with a more advanced AI in order to improve performance in the domain. Communication within computer games is something that we believe would improve the feelings of immersion that the player feels.

\paragraph*{\textit{Is there a time limit for solving the problem? I think, if given infinite time, random agent can always solve level1 and the average score should be 1.0.
When and how do agents fail to solve a problem?}}
The time limit for the problem was 2,000 ticks. Given infinite time, random agent can always solve any level. Some experiments (100,000 runs per level) showed a pair of random agents took on average this many ticks to complete each level:

\begin{tabular}{|l|l|c|}
\hline
\textbf{Old Map Name} & \textbf{New Map Name} & \textbf{Avg Ticks to complete} \\
\hline
level1.txt & SingleDoor & 7250\\
\hline
level1E.txt & Pathfinder & 419\\
\hline
level2.txt & SymmetricSingleDoor & 7353\\
\hline
level3.txt & ExtendedSide& 13416\\
\hline
level4.txt & SideBySide & 7302\\
\hline
level5.txt & Airlock & \\
\hline
level6.txt & Butterfly & \\
\hline
\end{tabular}

### 2015-08-06 Report/ceec.tex
Addded images to the thing, answered question about random and createed experiment to do so

\usepackage{graphicx}
\usepackage{glossaries}
\usepackage{verbatim}
\usepackage{array}
\usepackage{caption}
\captionsetup{belowskip=12pt,aboveskip=4pt}
\graphicspath{{stats-processing/}{stats-processing/data/maps/}}

@@

The starting positions for a simple problem is shown in Figure \ref{InitialState}
\begin{figure}[ht]
\centering
\includegraphics[scale=0.5]{InitialState}
\caption{Simple game state showing the different elements\protect\footnotemark }
\label{InitialState}
\end{figure}

\footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
All levels are defined by a simple text file format.

@@

\subsubsection{Maps}
The 7 maps that were included in the tournament were as follows:
\begin{itemize}
\item{\emph{SingleDoor} This map is the same as the map in \ref{InitialState}}
\item{\emph{Pathfinding} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
\item{\emph{SymmetricSingleDoor} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.}
\item{\emph{ExtendedSide} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game. Spreading the action parts away from the door and buttons was the main purpose of this one}
\item{\emph{SideBySide} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored. Each \emph{Agent} began in a separate room to each other instead of together.}
\item{\emph{Airlock} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}. Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.}
\item{\emph{Butterfly} This map was a new map - with two rooms each with a \emph{Goal} and a door. This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
\end{itemize}

>>>>

\usepackage{graphicx}
\usepackage{glossaries}
\usepackage{verbatim}
\usepackage{array}
\usepackage{caption}
\usepackage{float}
\captionsetup{belowskip=12pt,aboveskip=4pt}
\graphicspath{{stats-processing/}{stats-processing/data/maps/}}

@@

All levels are defined by a simple text file format.

@@

\subsubsection{Maps}
The 7 maps that were included in the tournament were as follows:

\paragraph{\emph{SingleDoor}} This map is a basic map with two rooms, single door and a button either side.
\begin{figure}[H]
\centering
\includegraphics[scale=0.35]{InitialState}
\caption{Single Door \protect\footnotemark}
\label{SingleDoor}
\end{figure}
\footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
\paragraph{\emph{Pathfinding}} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.
\begin{figure}[H]
\centering
\includegraphics[scale=0.35]{level1e}
\caption{Pathfinding}
\label{Pathfinding}
\end{figure}
\paragraph{\emph{SymmetricSingleDoor}} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.
\begin{figure}[H]
\centering
\includegraphics[scale=0.35]{level2}
\caption{Symmetric Single Door}
\label{SymmetricSingleDoor}
\end{figure}
\paragraph{\emph{ExtendedSide}} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game. Spreading the action parts away from the door and buttons was the main purpose of this one.
\begin{figure}[H]
\centering
\includegraphics[scale=0.35]{level3}
\caption{Extended Side}
\label{ExtendedSide}
\end{figure}
\paragraph{\emph{SideBySide}} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored. Each \emph{Agent} began in a separate room to each other instead of together.
\begin{figure}[H]
\centering
\includegraphics[scale=0.35]{level4}
\caption{Side By Side}
\label{SideBySide}
\end{figure}
\paragraph{\emph{Airlock}} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}. Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.
\begin{figure}[H]
\centering
\includegraphics[scale=0.35]{level5}
\caption{Airlock}
\label{Airlock}
\end{figure}
\paragraph{\emph{Butterfly}} This map was a new map - with two rooms each with a \emph{Goal} and a door. This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.
\begin{figure}[H]
\centering
\includegraphics[scale=0.35]{level6}
\caption{Butterfly}
\label{Butterfly}
\end{figure}
